Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-08 papers/ms.tex
update ms: h-alpha

Some salient stellar properties of the Kepler objects in Cep-Her can be gleaned
from Figure~\ref{fig:age}.  They span spectral types of G8V
(Kepler-1627) to K7V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$M0V.  And since a
Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ Myr \citep{choi_mesa_2016}, these
stars are all in the late stages of their pre-main-sequence
contraction.  Their heliocentric distances are $\approx$260\,pc
(KOI-7913 and KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in
RSG-5).

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K7V, while the secondary is $\approx$M0V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present in the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep[{\it e.g.},][]{kiman_calibration_2021}.  For
the primary, H$\alpha$ emission is also expected based on
previous spectroscopic studies of the Pleiades, IC~2602, and IC~2391
\citep[{\it e.g.},][their Figure~8]{stauffer_rotational_1997}.  Based
on the data from K.~Rocio et al's analysis\footnote{Available at
\url{https://zenodo.org/record/4659293\#.YkuKh27MKDV}}, a $\approx$K7V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    Kepler objects of interest compared to young open clusters and
    field stars. }
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    {\it Top}:
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018},
    where the quoted LDB age os from \citet{dahm_2015}.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure*}

>>>>

Some salient stellar properties of the Kepler objects in Cep-Her can be gleaned
from Figure~\ref{fig:age}.  They span spectral types of G8V
(Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And since a
Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ Myr \citep{choi_mesa_2016}, these
stars are all in the late stages of their pre-main-sequence
contraction.  Their heliocentric distances are $\approx$260\,pc
(KOI-7913 and KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in
RSG-5).

@@

Regarding indicators of youth, the primary has a spectral type
$\approx$K6V, while the secondary is $\approx$K8V.  At $\approx$40
Myr, lithium 6708\,\AA\ absorption is not expected for the secondary,
but might be present in the primary \citep[{\it
e.g.},][Figure~8]{soderblom_ages_2014}.  Conversely, H$\alpha$ is
expected to be in emission for for all M-dwarfs younger than
$\approx150$\,Myr \citep[{\it e.g.},][]{kiman_calibration_2021}.  For
the primary, H$\alpha$ emission is also expected based on
previous spectroscopic studies of the Pleiades, IC~2602, and IC~2391
\citep[{\it e.g.},][their Figure~8]{stauffer_rotational_1997}.  Based
on the data from K.~Rocio et al's analysis\footnote{Available at
\url{https://zenodo.org/record/4659293\#.YkuKh27MKDV}}, a $\approx$K6V
star should be emitting in H$\alpha$ at 40\,Myr, but not typically
past $\approx200\,{\rm Myr}$.  This presents a fairly direct test for
the star's age.

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and
    field stars. }
	Positive equivalent width means absorption; negative
	equivalent width means emission.
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    {\it Top}:
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure*}
